Edge sign prediction in general graphs and Correlation Clustering

### 2017-10-17 edge/conclusions.tex
edge: future directions

The framework we proposed is agnostic to the question of the interplay between connection and
linking attributes, although this is an interesting and active research question.

Homophily and Contagion Are Generically Confounded in Observational Social Network Studies
Cosma Rohilla Shalizi, Andrew C. Thomas
Sociological Methods \& Research
Vol 40, Issue 2, pp. 211-239
DOI: 10.1177/0049124111404820

Digital Footprints: Opportunities and Challenges for Online Social Research
Annual Review of Sociology
Vol. 40:129-152 
First published online as a Review in Advance on June 16, 2014
\url{https://doi.org/10.1146/annurev-soc-071913-043145}

Here is what the “Digital Footprints” writes about the previous paper
An important limitation is the difficulty distinguishing between homophily and contagion. Homophily
refers to a variety of selection mechanisms by which a social tie is more likely between individuals
with similar attributes and environmental exposures (McPherson et al.  2001). Contagion refers to
influence mechanisms (e.g., imitation or peer pressure) by which traits diffuse along network edges.
Homophily and contagion offer competing explanations for network autocorrelation, which refers to
the greater similarity in the attributes of closely connected nodes. Based on simulated networks,
Shalizi \& Thomas (2011, p. 216) conclude that “there is just no way to separate selection from
influence observationally” (see also Manski 1993). This does not mean that observational studies
using online networks are useless, but researchers need to refrain from assuming that the observed
network autocorrelation reflects contagion effects and to acknowledge that the similarity between
adjacent nodes may reflect the mutually reinforcing effects of influence and selection whose
separate contributions may be impossible to tease apart.  For example, although Ugander et al.
(2012) controlled for demographic similarity (sex, age, and nationality), there are countless other
ways in which shared environments, affiliations, interests, and personality traits might cause two
friends to join Facebook independently but not on the same day, making it look like the “early
adopter” influenced the friend they invited who would have joined anyway.

Furthermore, we could also consider the role of time with dynamic networks. For instance, while the
photo similarity between two Flickr users rises before they connect, it later decreases if they have
the same level of popularity, as they try to differentiate themselves
Zeng and Wei: Social Ties and User Content Generation: Evidence from Flickr, Information Systems
Research 24(1), pp. 71–87

>>>>

\section{Conclusions}
\label{sec:edge_conc}

We could extend our approach to more general types of graphs and tasks:

\begin{itemize}[leftmargin=*]

  \item First, as we mentioned earlier, \textbf{networks are dynamic} and evolve over time, with
    nodes and edges constantly appearing and disappearing~\autocite{networkEvolution14}. Slicing
    time into successive periods is one way to create edge types, one per period. For instance,
    \textcite{TimedUSSenate10} study the \np{110} congresses of the US senate between the years 1789
    and 2008, where \np{1884} individual Senators are linked by their voting similarity, and show
    how it improves the detection of relevant communities. Beyond predicting the relative order of
    links, it would also be interesting to include time into nodes similarity itself.
    %
    For instance, while the photo similarity between two Flickr users rises before they connect, it
    later decreases if they have the same level of popularity, as both try to differentiate
    themselves~\autocite{dynamicFlickr13}.
    %
    More generally, by defining our problem on a static snapshot of a graph, our model is agnostic
    to the question of whether edges were created because of the similarity/dissimilarity of
    the linked nodes' attributes or because attributes started to change after the edge creation.
    This is traditionally framed as dichotomy between homophily and contagion, and is an active topic
    of research in social networks analysis~\autocites{InfluenceVsHomo08}{ConfoundedHomophily11} as
    noted by \textcite{OSNreview14}: \textquote{Homophily refers to a variety of selection
    mechanisms by which a social tie is more likely between individuals with similar attributes and
    environmental exposures~\autocite{Homophily01}. Contagion refers to influence mechanisms (\eg{}
    imitation or peer pressure) by which traits diffuse along network edges. Homophily and contagion
    offer competing explanations for network autocorrelation, which refers to the greater similarity
    in the attributes of closely connected nodes.}

  \item Another rich class of graphs were predicting edge types would be a challenging and rewarding
    task is \textbf{multigraph}, which allow several edges between two nodes. It can also be seen as
    the flattening of several graphs sharing the same nodeset, but where the provenance of each edge
    would have been lost and need to be recover. With our original formulation of goodness as
    ${s_{uv}}^T w_{uv}$, only one direction can achieve the higher score (discarding the rare case
    of tie). One alternative we proposed was to let each $w_{uv}$ be a linear combination of a small
    number of base directions, although experimentally it did not fit well our synthetic data.
    Symmetrically, another idea could be to have more than one way to compute the similarity
    $s_{uv}$ between two nodes.

  \item Generalizing the balance theory from signed graphs, we could imagine that in triangles or
    short cycles, only certain combinations of directions are valid (or at least desirable).
    Interestingly, this would likely require different optimization algorithms, probably non convex.
    However, while this is a general concept, its exact implementation might be
    application-dependant. Furthermore, in our current setting, we do not know in advance in the
    semantic of each direction, and we have no labeled edges. Therefore, it is not clear how those
    constraints would be specified or whether they can be learned, if applicable. A limited solution
    exists in the context of heterogeneous information networks, where in addition to having several
    types of edges, there are also several types of nodes. Since not all type of node can be
    connected with any type of edges, the possible connections are themselves represented as a meta
    graph called the network schema~\autocite[Definition 3]{HINSurvey17}. This approach would need
    to be extended to deal with higher order patterns.

  \item Among tasks that could benefit from labeling the edge of complex networks, we mention two.
    The first is \textbf{graph summarization} where the idea is to transmit a fraction of a large
    graph plus additional information that can be used to reconstruct the original graph. Namely,
    our goal here is to send only a few node profiles along with the edge directions, enabling the
    missing profiles to be reconstructed from the known goodness values. Note that we spare
    information regarding the profiles but still transmit the full topology. Therefore, this differs
    from lossless schemes~\autocites{compressSN09}{compressSN12} that leverage typical edge locality
    patterns to encode edges using as few bits as possible, or from lossy graph sketching
    methods~\autocite{graphSketch12} discussed in \autoref{sub:gtx_state_of_the_art}, which preserve
    spectral and topological properties of the original graph.
    %
    The second is \textbf{node embedding}, where every node $u$ is represented by a vector of size
    $k$ containing the relative proportion of each direction with the edges incident to $u$.
\end{itemize}
